\documentclass[10.5pt]{article}
\usepackage[a4paper,top=0.4in,bottom=0.4in,left=0.45in,right=0.45in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}

\titleformat{\section}{\normalsize\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{5pt}{3pt}

\hypersetup{colorlinks=true,urlcolor=black,linkcolor=black}

\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}

\newcommand{\blist}{\begin{itemize}[leftmargin=*,noitemsep,topsep=1pt,parsep=0pt,itemsep=1pt]}
\newcommand{\elist}{\end{itemize}\vspace{3pt}}

\begin{document}

% Header
\begin{center}
    {\huge\textbf{\scshape Swayam Dani}} \\[1pt]
    \small
    341-224-3555 $|$
    \href{mailto:sdani@ucsd.edu}{sdani@ucsd.edu} $|$
    \href{https://www.linkedin.com/in/swayam-dani}{LinkedIn} $|$
    \href{https://github.com/swayamdani}{GitHub} $|$
    \href{https://www.swayamdani.com}{swayamdani.com}
\end{center}
\vspace{-4pt}

% Education
\section*{Education}
\textbf{University of California, San Diego} \hfill San Diego, CA \\
\textit{Bachelors of Science in Computer Science} \hfill \textit{Expected June 2027} \\[-2pt]
\small \textbf{Coursework:} Algorithms, Data Structures, Systems Programming, Probability \& Statistics, Databases, Cybersecurity
 

% Technical Skills
\section*{Technical Skills}
\small
\textbf{Languages:} Python, C++, Java, JavaScript, TypeScript, SQL \\[-1pt]
\textbf{Quant / Data:} NumPy, pandas, scikit-learn, PyTorch, Hugging Face, sentence-transformers, pgvector, TimescaleDB \\[-1pt]
\textbf{Systems \& Backend:} FastAPI, Asyncio, PostgreSQL, Redis, Docker, Railway, REST APIs, JWT, Argon2 \\[-1pt]
\textbf{Tools \& Workflow:} Git, GCP, Streamlit, Next.js, React, cross-functional collaboration, technical documentation \\
\textbf{Software:} Office 365, Figma, Jira, Adobe Suite 

% Projects
\section*{Relevant Experience}
\small

\textbf{HandsInTech --- AI/ML Intern} \hfill \textit{June 2025 -- September 2025}
\blist
    \item Architected a political intelligence engine using LoRA-adapted LLaMA 3.1-8B with RAG; collaborated with a cross-functional team to integrate real-time crawled data, election datasets, and document intelligence pipelines.
    \item Delivered weekly technical updates to stakeholders; proactively documented system design decisions and adapted the architecture based on team feedback in a fast-moving research environment.
\elist

\textbf{AlphaLens --- Quantitative Signal Research Platform --- Developer} \hfill \textit{February 2026 -- Present} \\ \textit{Python, FastAPI, TimescaleDB, pgvector}
\blist
    \item Built an end-to-end quant research pipeline: async news crawler $\rightarrow$ semantic embedding (sentence-transformers + pgvector IVFFlat) $\rightarrow$ signal generation $\rightarrow$ real-time Telegram alerts for a 50-stock universe.
    \item Engineered NLP-driven alpha features from financial news; tracked information coefficient (IC) and signal decay to evaluate signal quality and persistence across the Nifty50.
    \item Architected a multi-service system (crawler, AI-worker, notifier, API) coordinated via PostgreSQL; deployed on Railway with TimescaleDB for time-series signal storage and backtesting.
    \item Independently scoped and executed the full research-to-production cycle --- from signal ideation and feature engineering to deployment and monitoring --- adapting quickly as data characteristics shifted.
\elist

\textbf{Swarm --- Federated AI Workspace  --- Team Lead/Developer} \hfill \textit{March 2026} \\ \hfill \textit{Python, FastAPI, Ollama, RAG, MCP} \hfill \textit{\small Qualcomm Multiverse Hackathon}
\blist
    \item Collaborated with a teammate under tight deadlines to design and ship a privacy-first federated inference system: local LLM nodes orchestrated by a coordinator agent routing queries via federated RAG with no data leaving the local network.
    \item Owned the backend MCP integrations (Gmail, Calendar, Slack, GitHub, Notion) enabling cross-source personal data queries with zero-egress guarantees; coordinated system interfaces with teammate's Next.js frontend.
    \item Designed relay server architecture on Railway for peer discovery and session routing without centralizing user data; adapted the architecture mid-hackathon in response to latency constraints discovered during testing.
\elist

\textbf{Political Intelligence Engine --- LoRA-Adapted LLM + RAG --- Python Developer} \hfill \textit{June 2025 - September 2025} \\ \hfill \textit{Python, FastAPI, LLaMA 3.1}
\blist
    \item Architected a domain-specific intelligence engine fine-tuned via LoRA on LLaMA 3.1-8B with real-time crawled data, regional election datasets, and multi-source document pipelines; presented findings and design decisions to senior stakeholders weekly.
    \item Built async FastAPI backend supporting session-aware inference, structured analytics logging, and multi-source correlation; documented system architecture and API contracts for team-wide use.
\elist

\textbf{Crawlit --- Async Web Crawling Framework  --- Developer} \hfill \textit{May 2025 - June 2025} \\ \hfill \textit{Python, Asyncio, SQLite}
\blist
    \item Designed a production-grade async crawling library with authenticated sessions, adaptive rate limiting, fault tolerance, and resumable crawl state persistence via SQLite.
    \item Maintained public documentation and a structured issue tracker; resolved a 31-issue audit through iterative testing and peer review, improving reliability and code quality across the library.
\elist

\textbf{Password Security Assessment Platform  --- Developer} \hfill \textit{March 2025 - May 2025} \\ \hfill \textit{Python, FastAPI, React, Redis}
\blist
    \item Full-stack security tool evaluating breach exposure via k-Anonymity APIs; implemented Argon2 hashing, Redis caching, and JWT stateless auth with real-time analytics dashboards.
    \item Designed system to be extensible and well-documented for future contributors; applied security best practices validated through structured code review.
\elist

\section*{Other Experience}
\small
\textbf{Marketing Operations Intern} --- BCOE, UC Riverside \hfill \textit{Jul 2025 -- Sep 2025}
\blist
    \item Redesigned Monday.com workflows and cross-team dashboards to improve execution visibility; produced standardized templates adopted across multiple concurrent initiatives.
\elist

\textbf{Engineering Ambassador} --- BCOE, UC Riverside \hfill \textit{Apr 2024 -- Jun 2025}
\blist
    \item Represented the College of Engineering at outreach events; collaborated with student teams on event planning, communications, and digital engagement campaigns.
\elist

\end{document}